---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(maocpf)
```

The goal of maocpf is to pull candidate fundraising data from the Massachusetts Office of Campaign and Political Finance.

Here's a typical workflow.

## Setup: Once or infrequently

1) Get a list of all local candidates with `get_local_candidates()`. This function downloads a file with all candidates from the MA OCPF Web site to a temp subdirectory (which will be created if it doesn't exist). You can filter by city and/or office, but it's probably better to stick to the default and download the full list once. Then you can filter that unless you are 100% sure you only want the filtered version. The file downloads each time you run this function. 

2) Get the IDs of the candidates you want with `get_candidate_id()` using the candidate name as the first argument and the data frame you created in step 1 as the second argument. _Store this data somewhere for re-use!_

Here is a sample workflow to begin using this package:

```{r eval=FALSE}

all_candidate_info <- get_local_candidates()
save(all_candidate_info, "data/all_candidate_info.Rdata")

all_framingham_candidates <- dplyr::filter(all_candidate_info, Candidate_City == "Framingham")
save(all_framingham_candidates, "data/all_framingham_candidates.Rdata")


```

Note that for state legislative districts that encompass areas outside of one community, you'll want to filter by District column instead. 

Data for `all_candidate_info` and `all_framingham_candidates` from February 14, 2021 are included with this package.

## Run regularly

To get up-to-date data on a candidate, use the `get_candidate_contribution_data()` function with the candidate's ID. For example, I can find Framingham Mayor Spicer's ID with the get_candidate_id() function and all or part of her name:


```{r,  message=FALSE, warning=FALSE}
get_candidate_id("Spicer")
```

Now I can pull all the contributions since the start of 2021 with 

```{r, eval=FALSE}
spicer_contributions <- get_latest_candidate_contributions("16676", "2021-01-01")

```

